### 2013-09-15 fig_mr_arfi_weight.tex
updated text for corrected prostate weights and ellipsoidal volumes

\begin{figure}[htb!]
\centering
\begin{tabular}{ll}
\includegraphics[width=0.33\linewidth]{figs/corr_weight_vol.pdf} &
\includegraphics[width=0.33\linewidth]{figs/corr_pathVol_vol.pdf} \\
(a) Image Volume : Prostate Weight & (b) Image Volume : Pathology Volume \\
\end{tabular}
\caption{The prostates analyzed in this study showed no significant correlation
    between their measured excised pathology weight (a) and the reconstructed
    volumes in T2WI MR (blue) and ARFI imaging (green).  The coefficients of
    determination (R$^2$) for the linear regressions for each imaging modality
    were 0.05 and 0.13, respectively, indicating no significant correlation.
    Tri-axial pathology measurements were used to make an ellipsoidal prostate
    volume approximation (b), which showed mild correlation with T2WI MR (R$^2$
    = 0.32) and moderate correlation with ARFI imaging (R$^2$ = 0.71).}
\label{fig:mr_arfi_weight} 
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tabular}{lll}
\includegraphics[width=0.3\linewidth]{figs/corr_path_vol_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol} \\
(a) Path Weight : Path Volume & (b) Image Volume : Prostate Weight & (c) Image Volume : Path Volume \\
\end{tabular}
\caption{Tri-axial pathology measurements were used to make an ellipsoidal
    prostate volume approximation based on gross pathology axis measurements,
    which was moderately well-correlated with the excised prostated weights (a,
    R$^2$ = 0.68).  T2WI MR (blue, X) showed a moderate correlation between the
    reconstructed volumes and prostate weight (R$^2$ = 0.44), while volumes
    reconstructed from ARFI images (green, O) showed weaker correlation (R$^2$
    = 0.21) (b).  Even weaker correlations existed between both T2WI MR and
    ARFI image volumens and approaximated ellipsoidal prostate pathology
    volumes (R$^2$ = 0.08 and 0.01, respectively) (c).}
\label{fig:mr_arfi_weight}
\end{figure}

### 2013-09-15 results.tex
added weight : ellipsoidal volume to text and figs
updated text for corrected prostate weights and ellipsoidal volumes

MR and ARFI imaging total prostate volumes were also compared with the weights
and prostate volumes, approximated to be tri-axial ellipsoids, and calculated
from measurements of the prostate semi-principal axes.  That was no significant
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:fig_mr_arfi_weight}, R$^2$ = 0.05 (MR) and 0.13
(ARFI)), and there was XXXX correlation with the ellipsoidal approximation of
the measurement prostate volume and the image-recontructed volumens (Figure
XX).

>>>>

MR and ARFI imaging total prostate volumes were also compared with the weights
and prostate volumes, approximated to be tri-axial ellipsoids, and calculated
from measurements of the prostate semi-principal axes.  Prostate weights were
moderately correlated with estimated pathology ellipsoidal prostate volumes
(Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = 0.68).  There was moderate
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$ = 0.44 (MR) and 0.21
(ARFI)), though there was weaker correlation with the ellipsoidal approximation
of the measurement prostate volume and the image-recontructed volumens
(Figure~\ref{fig:mr_arfi_weight}(c), R$^2$ = 0.08 (MR) and 0.01 (ARFI)).
